Analysis paper

### 2021-06-19 analysis/analysis.Rmd
create new plots for comparing locations

@@

# sharpness of performance
p_sharpness <- scores %>%
  ggplot(aes(x = horizon, y = sharpness, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  labs(y = "sharpness", x = NULL) + 
  theme_minimal()

@@

p_cov50 <- scores[range %in% c(50)] %>%
  ggplot(aes(x = horizon, y = coverage, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type) + 
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  scale_color_manual(values = coldeaths) + 
  labs(y = "Empirical coverage", x = "Forecast horizon") + 
  theme_minimal() + 
  expand_limits(y=c(0, 1)) + 
  theme(legend.position = "bottom") + 
  scale_y_continuous(labels = scales::percent)

@@

p_cov90 <- scores[range %in% c(90)] %>%
  ggplot(aes(x = horizon, y = coverage, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type) + 
  theme_minimal() + 
  theme(legend.position = "bottom") + 
  geom_hline(yintercept = 0.90, linetype = "dashed") +
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  labs(y = "Empirical coverage", x = "Forecast horizon") + 
  expand_limits(y=c(0, 1)) + 
  scale_y_continuous(labels = scales::percent)

@@

```{r}
scores <- eval_forecasts(filtered_data[model %in% 
                                         ensemble_models[!grepl("mean", ensemble_models)]], 
                         summarise_by = c("model", "target_type", "horizon"), 
                         quantiles = 0.5, 
                         sd = TRUE)

>>>>

### Aggregate performance across different horizons

@@

# sharpness of performance
p_sharpness <- scores %>%
  ggplot(aes(x = horizon, y = sharpness, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  labs(y = "Sharpness", x = NULL) + 
  theme_minimal()

@@

p_cov50 <- scores[range %in% c(50)] %>%
  ggplot(aes(x = horizon, y = coverage, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type) + 
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  scale_color_manual(values = coldeaths) + 
  labs(y = "Coverage - 50% PI", x = "Forecast horizon") + 
  theme_minimal() + 
  expand_limits(y=c(0, 1)) + 
  theme(legend.position = "bottom") + 
  scale_y_continuous(labels = scales::percent)

@@

p_cov90 <- scores[range %in% c(90)] %>%
  ggplot(aes(x = horizon, y = coverage, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type) + 
  theme_minimal() + 
  theme(legend.position = "bottom") + 
  geom_hline(yintercept = 0.90, linetype = "dashed") +
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  labs(y = "Coverage - 90% PI", x = "Forecast horizon") + 
  expand_limits(y=c(0, 1)) + 
  scale_y_continuous(labels = scales::percent)

@@

### Aggregate performance across locations

```{r}
scores <- eval_forecasts(filtered_data[model %in% regular_models & horizon == 2], 
                         summarise_by = c("model", "target_type", "location_name"), 
                         quantiles = 0.5, 
                         sd = TRUE)

# mean performance
p_mean <- scores %>%
  ggplot(aes(x = location_name, y = interval_score, group = model, color = model)) + 
  geom_point() + 
  geom_line(linetype = "dashed", size = 0.3) + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme_minimal() + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  labs(y = "mean WIS", x = NULL)

# mean performance
p_mean <- scores %>%
  ggplot(aes(x = location_name, y = interval_score, group = model, color = model)) + 
  geom_point() + 
  geom_line(linetype = "dashed", size = 0.3) + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme_minimal() + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  labs(y = "mean WIS", x = NULL)

# median performance
p_median <- scores %>%
  ggplot(aes(x = location_name, y = interval_score_0.5, group = model, color = model)) + 
  geom_point() + 
  geom_line(linetype = "dashed", size = 0.3) + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  labs(y = "median WIS", x = NULL) + 
  theme_minimal()

# sd of performance
p_wis_sd <- scores %>%
  ggplot(aes(x = location_name, y = interval_score_sd, group = model, color = model)) + 
  geom_point() + 
  geom_line(linetype = "dashed", size = 0.3) + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  labs(y = "WIS - sd", x = NULL) + 
  theme_minimal()

# sharpness of performance
p_sharpness <- scores %>%
  ggplot(aes(x = location_name, y = sharpness, group = model, color = model)) + 
  geom_point() + 
  geom_line(linetype = "dashed", size = 0.3) + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  labs(y = "Sharpness", x = NULL) + 
  theme_minimal()

# absolute error of performance
p_aem <- scores %>%
  ggplot(aes(x = location_name, y = aem, group = model, color = model)) + 
  geom_point() + 
  geom_line(linetype = "dashed", size = 0.3) + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  labs(y = "Absolute error", x = NULL) + 
  theme_minimal()

# bias
p_bias <- scores %>%
  ggplot(aes(x = location_name, y = bias, group = model, color = model)) + 
  geom_point() + 
  geom_line(linetype = "dashed", size = 0.3) + 
  facet_wrap(~ target_type) + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  expand_limits(y=c(-0.2, 0.2)) + 
  labs(y = "Bias", x = NULL) + 
  theme_minimal()

# coverage
scores <- eval_forecasts(filtered_data[model %in% regular_models], 
                         summarise_by = c("model", "target_type", "location_name", "range"), 
                         quantiles = 0.5, 
                         sd = TRUE)

p_cov50 <- scores[range %in% c(50)] %>%
  ggplot(aes(x = location_name, y = coverage, group = model, color = model)) + 
  geom_point() + 
  geom_line(linetype = "dashed", size = 0.3) + 
  facet_wrap(~ target_type) + 
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  scale_color_manual(values = coldeaths) + 
  labs(y = "Coverage - 50% PI", x = "Location") + 
  theme_minimal() + 
  expand_limits(y=c(0, 1)) + 
  theme(legend.position = "bottom") + 
  scale_y_continuous(labels = scales::percent)

p_cov90 <- scores[range %in% c(90)] %>%
  ggplot(aes(x = location_name, y = coverage, group = model, color = model)) + 
  geom_point() + 
  geom_line(linetype = "dashed", size = 0.3) + 
  facet_wrap(~ target_type) + 
  theme_minimal() + 
  theme(legend.position = "bottom") + 
  geom_hline(yintercept = 0.90, linetype = "dashed") +
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  labs(y = "Coverage - 90% PI", x = "Location") + 
  expand_limits(y=c(0, 1)) + 
  scale_y_continuous(labels = scales::percent)

ggsave(here("analysis", "plots", "aggregate-performance-2-weeks-locations-all.png"), 
       height = 9.1, width = 10)

}
```{r}
scores <- eval_forecasts(filtered_data[model %in% 
                                         ensemble_models[!grepl("mean", ensemble_models)]], 
                         summarise_by = c("model", "target_type", "horizon"), 
                         quantiles = 0.5, 
                         sd = TRUE)
